### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
replaced the R package citations in the original bib file with those from the r-references.bib file, including the references in text.

# manually retrieving the Rstudio version

### DON'T FORGET THAT I SHOULD REMOVE HERE THE R PACKAGE REFERENCES FROM MY REFERENCES BIB AND SHOULD HAVE THE R=REFERENCES BIB TAKE CARE OF THAT INSTEAD.
```

This is an example of a non-essential citation [\@ @vanlissaWORCS2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

@@

Two different types of score reliabilities were calculated: Cronbach's alpha and omega. Cronbach's alpha was used as it is one of the most popular indices of score reliability [@cho2015cronbach]. Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@revelle2022psych]. Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.

@@

Thus for testing hypothesis 1, instead of comparing the reported Cronbach's alpha coefficient between original and replication, the total number of reported reliability coefficients were compared instead. This total also included reliability coefficients other than Cronbach's alpha. This comparison was implemented via a chi-square test using the base R stats package [@R2021R].

@@

Using the lmer function from the lme4 package [@bates2015lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set. The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:

@@

Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio. In order to model a ratio dependent variable, beta regression was used. Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results. What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios. Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta]. The beta regression model was implemented using the betareg function within the betareg package [@cribari2010beta]. Defaults were used for all function parameters besides the model formula and data. All beta regression models used the beta link function, which is as follows:

@@

These models had independence of observations as another assumption, the observations here referring to a replication set. this is known to be false since the data is nested within four separate Many Labs projects. In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models were implemented as sensitivity analyses for the tests of both hypothesis 5 & 6. In these models each replication set was treated as being nested in its respective Many Labs project. Worth noting is that currently the betareg package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@bates2015lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.

@@

Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set. A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@revelle2022psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.

>>>>

# manually retrieving the Rstudio version
RStudio.Version()
```

@@

Two different types of score reliabilities were calculated: Cronbach's alpha and omega. Cronbach's alpha was used as it is one of the most popular indices of score reliability [@cho2015cronbach]. Omega was added to the analysis as it has been argued to be a more informative measure of score reliability, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Cronbach's alpha and omega were calculated using the alpha and omega functions respectively in the psych R package [@R-psych]. Default arguments were used for both functions except the nfactors in the omega function, which was set to 1.

@@

Thus for testing hypothesis 1, instead of comparing the reported Cronbach's alpha coefficient between original and replication, the total number of reported reliability coefficients were compared instead. This total also included reliability coefficients other than Cronbach's alpha. This comparison was implemented via a chi-square test using the base R stats package [@R-base].

@@

Using the lmer function from the lme4 package [@R-lme4], a multilevel null model with the Cronbach's alpha or omega coefficient of a replication as dependent was specified, where the random intercept was grouped by replication set. The formulas for this model, where $alpha_{ij}$ represents the calculated Cronbach's alpha coefficient of a single study at one lab location with $i = 1,..., n_{locations}$ and $j = 1,...,n_{replications}$ look as follows:

@@

Hypothesis 4, 5, & 6 were all tested using a model with the same dependent variable: total QMP ratio. In order to model a ratio dependent variable, beta regression was used. Beta regression models operate similarly to standard generalized linear models with similar interpretations of the results. What differentiates them is that they are suitable to model dependent variables with values in the interval of $(0, 1)$, meaning ratios. Furthermore, they are well suited for modelling heteroskedastic and asymmetrically distributed dependent variables [@cribari2010beta]. The beta regression model was implemented using the betareg function within the betareg package [@R-betareg_a; @R-betareg_b]. Defaults were used for all function parameters besides the model formula and data. All beta regression models used the beta link function, which is as follows:

@@

These models had independence of observations as another assumption, the observations here referring to a replication set. this is known to be false since the data is nested within four separate Many Labs projects. In order to test if this nested structure might influence the relations described in hypothesis 5 & 6, random intercept and random slope multilevel models were implemented as sensitivity analyses for the tests of both hypothesis 5 & 6. In these models each replication set was treated as being nested in its respective Many Labs project. Worth noting is that currently the betareg package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the lmer function from the lme4 package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the betareg package) to better fit the Gaussian model.

@@

Finally, in order to present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set. A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.
